# Introduction {#intro}

Let's make a short introduction for BEFORE the first class.

Outline: 

* A brief definition of programming and programming language.
* Why would you want to learn programming, and specifically using R.
* How to install R and Rstudio.
* Rstudio IDE
  + The R console: Writing your first lines of R code.
  + The text editor: Saving your code.
  + Other windows and tabs: Environment, Files, Plots, and Help.
* Saving your code, objects and session.

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway.

This is an example of how to make a fiure with captions and other parameters.

```{r iris-fig, fig.cap='The iris dataset.', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(iris, col = iris$Species, main = "The iris dataset", pch = 16)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., 
see Figure \@ref(fig:iris-fig). 

Similarly, you can reference tables generated from `knitr::kable()`, e.g., 
see Table \@ref(tab:iris-tab).

```{r iris-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** 
package [@R-bookdown] in this sample book, which was built on top of R 
Markdown and **knitr** [@xie2015]. Bibliography is saved on .bib files in the
main directory, in this case packages bibliography is created on the
"packages.bib" file.
